A hazards approach to the biometric analysis of infant mortality

### 2023-04-05 Slides/slides.Rmd
polishing slides

$t$ is age in days.

@@

@@

\tiny

@@

@@

@@

@@

@@

## Exogenous mortality on the normal time scale

@@

\emp{Skåne} 1711--1800

@@

@@

@@

**R** code for this paper and talk.

>>>>

$t$ is \emp{age in days}.

@@

Calculation (no ties): $(2, \frac{1}{100}), (6, \frac{2}{100}), (10, \frac{3}{100}), \ldots, (309, \frac{10}{100}).$

@@

@@

Total mortality: $1 - \exp(-0.106) \approx 0.101$.

Excellent fits!

@@

Total mortality: $1 - \exp(-0.056) \approx 0.054$.

Excellent fits!

@@

The log-cube model \emp{does not fit} at all, despite \emp{high-quality} data!

\emp{Too old} time period?

@@

*   Reasonable linear post-neonatal fit.
*   But \emp{no} room for \emp{endogenous} mortality.
*   Many \emp{early deaths missing}.

@@

\emp{NOTE:} $H(t; \lambda)$ is the \emp{log-cube transform!}

## Exogenous mortality on the natural time scale

@@

\emp{Skåne} 1711--1800.

@@

\emp{Decent fit} if we skip the log-cube distribution!

@@

**R** code for this paper:

@@
